Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010

### 2017-01-06 ms.tex
I added another plot for the residuals using the 3 term model.

\begin{figure}
\begin{centering}
\includegraphics[width=0.7\textwidth]{corner_fit_2term.pdf}
\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfitMultiTerm} for 2 terms.
Again, there is little correlation between the posteriors for the different parameters.}\label{fig:post2Cosfit}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{residual_ML.pdf}
\caption{Residuals after subtracting the maximum likelihood model from Equation \ref{eq:cosfitMultiTerm} from the data. The standard deviation of the residuals is 0.6\% whereas the error from photon counting statistics is 0.2\%.}\label{fig:resid2Cosfit}
\end{centering}
\end{figure}

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=0.7\textwidth]{corner_fit_2term.pdf}
\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfitMultiTerm} for 2 terms.
Again, there is little correlation between the posteriors for the different parameters. {\it Right} Same figure, but with 3 cosine terms.}\label{fig:post2Cosfit}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.48\textwidth]{residual_2term_1080nm.pdf}
\includegraphics[width=0.48\textwidth]{residual_3term_1080nm.pdf}
\caption{{\it Left:} Residuals after subtracting the maximum likelihood model from Equation \ref{eq:cosfitMultiTerm} from the data. The standard deviation of the residuals is 0.6\% whereas the error from photon counting statistics is 0.2\%.}\label{fig:resid2Cosfit}
\end{centering}
\end{figure}
